Modelling biological pathway dynamics\\with \tas

### 2013-07-01 Paper.tex
Scale now changed to Blue-Yellow-Red. Also, some text adjustments

\definecolor{ourBlue}{rgb}{0, 0.8, 0.8}
\renewcommand{\tabcolsep}{2mm}
\begin{table}[htbp]
\caption{Lower and upper bounds for a reaction $A \rightarrow B$ with kinetic scenario 2, $k = 0.004$ (corresponding to the \emph{medium} preset)
and 10 seconds per UPPAAL time step. Granularity of $A$ is 5 (i.e. 5 activation steps from 0 to maximum activity), granularity of $B$ is 3. In both cases,
0 means completely inactive. With these settings, $\mbox{\it levelsScale} = 5.0$ and $\mbox{\it timeScale} = 0.1$. Uncertainty is set at $5 \%$.
{\color{BrickRed}Red} numbers are lower bounds, {\color{ourBlue} cyan} numbers are upper bounds.}\label{tab:lower-upper-bounds}
\centering
    \begin{tabular}{|c||c|c|c|c|c|c|}
      \hline
      {\backslashbox[2em]{$B$\kern-2em}{\kern-1em$A$}} & \makebox[.5em]{0} & \makebox[.5em]{1} & \makebox[.5em]{2} & \makebox[.5em]{3} & \makebox[.5em]{4} & \makebox[.5em]{5} \\
      \hline\hline
      \begin{minipage}[c][1em][c]{1em}\centering 0\end{minipage} & \makebox[.5em]{$\infty$} & [{\scriptsize\color{BrickRed}40}, {\scriptsize\color{ourBlue}44}] & [{\scriptsize\color{BrickRed}20}, {\scriptsize\color{ourBlue}22}] & [{\scriptsize\color{BrickRed}13}, {\scriptsize\color{ourBlue}15}] & [{\scriptsize\color{BrickRed}10}, {\scriptsize\color{ourBlue}11}] & [{\scriptsize\color{BrickRed}8}, {\scriptsize\color{ourBlue}9}] \\
      \hline
      \begin{minipage}[c][1em][c]{1em}\centering 1\end{minipage} & \makebox[.5em]{$\infty$} & [{\scriptsize\color{BrickRed}59}, {\scriptsize\color{ourBlue}66}] & [{\scriptsize\color{BrickRed}30}, {\scriptsize\color{ourBlue}33}] & [{\scriptsize\color{BrickRed}20}, {\scriptsize\color{ourBlue}22}] & [{\scriptsize\color{BrickRed}15}, {\scriptsize\color{ourBlue}16}] & [{\scriptsize\color{BrickRed}12}, {\scriptsize\color{ourBlue}13}] \\
      \hline
      \begin{minipage}[c][1em][c]{1em}\centering 2\end{minipage} & \makebox[.5em]{$\infty$} & [{\scriptsize\color{BrickRed}119}, {\scriptsize\color{ourBlue}131}] & [{\scriptsize\color{BrickRed}59}, {\scriptsize\color{ourBlue}66}] & [{\scriptsize\color{BrickRed}40}, {\scriptsize\color{ourBlue}44}] & [{\scriptsize\color{BrickRed}30}, {\scriptsize\color{ourBlue}33}] & [{\scriptsize\color{BrickRed}24}, {\scriptsize\color{ourBlue}26}] \\
      \hline
      \begin{minipage}[c][1em][c]{1em}\centering 3\end{minipage} & \makebox[.5em]{$\infty$} & $\infty$ & $\infty$ & $\infty$ & $\infty$ & $\infty$\\
      \hline
    \end{tabular}
\end{table}

@@

\begin{figure}[htb]
\centering
  \includegraphics[width=.48\textwidth]{mapk_model_egf7}
\caption{The model represented in the ANIMO user interface.
The \emph{Network} central panel represents the model as the classical nodes-edges network
familiar in biology. To this representation, node colours and shapes are added %in order
to represent current activity levels and protein categories, as defined in the \emph{Legend}
panel on the left. On the right, the \emph{Results Panel} shows a graph of the activities
of selected nodes during the user-chosen interval of 60 minutes.
A vertical red bar, which can be moved with the underlying slider, indicates the point in
the simulation trace on which the colouring of the nodes in the \emph{Network} panel is based.
The graph allows the user to visually compare simulation results with experimental data.
The {\sf Erk (EGF) data} series is based on experimental data from Santos et al.~\cite{egf-ngf}.
}\label{fig:case-study-model}
\end{figure}

@@

\begin{figure}[htb]
\centering
  \includegraphics[width=.48\textwidth]{mapk_model_diff4}
\caption{Difference between the simulations obtained using
50 ng/ml NGF and 100 ng/ml EGF as input at 22 minutes (vertical red bar in right panel). In this mode, node colours
are based on the difference of activity between the two configurations of the model:
a cyan-coloured node is more active due to NGF treatment, while red indicates less activity and white
means no difference. Note that NGF and EGF are both white, since at 22 minutes, 
NGF and EGF are inactivated in both conditions by the neutralizing antibody. A slider underneath the graph can be used to 
interactively view the differences at different time points. \label{fig:case-study-diff}}
\end{figure}

>>>>

\definecolor{ourBlue}{rgb}{0, 0.8, 0.8}
\renewcommand{\tabcolsep}{2mm}
\begin{table}[htbp]
\caption{Lower and upper bounds for a reaction $A \rightarrow B$ with kinetic scenario 2, $k = 0.004$ (corresponding to the \emph{medium} preset)
and 10 seconds per UPPAAL time step. Granularity of $A$ is 5 (i.e. 5 activation steps from 0 to maximum activity), granularity of $B$ is 3. In both cases,
0 means completely inactive. With these settings, $\mbox{\it levelsScale} = 5.0$ and $\mbox{\it timeScale} = 0.1$. Uncertainty is set at $5 \%$.
{\color{ourBlue} cyan} numbers are lower bounds, {\color{BrickRed}Red} numbers are upper bounds.}\label{tab:lower-upper-bounds}
\centering
    \begin{tabular}{|c||c|c|c|c|c|c|}
      \hline
      {\backslashbox[2em]{$B$\kern-2em}{\kern-1em$A$}} & \makebox[.5em]{0} & \makebox[.5em]{1} & \makebox[.5em]{2} & \makebox[.5em]{3} & \makebox[.5em]{4} & \makebox[.5em]{5} \\
      \hline\hline
      \begin{minipage}[c][1em][c]{1em}\centering 0\end{minipage} & \makebox[.5em]{$\infty$} & [{\scriptsize\color{ourBlue}40}, {\scriptsize\color{BrickRed}44}] & [{\scriptsize\color{ourBlue}20}, {\scriptsize\color{BrickRed}22}] & [{\scriptsize\color{ourBlue}13}, {\scriptsize\color{BrickRed}15}] & [{\scriptsize\color{ourBlue}10}, {\scriptsize\color{BrickRed}11}] & [{\scriptsize\color{ourBlue}8}, {\scriptsize\color{BrickRed}9}] \\
      \hline
      \begin{minipage}[c][1em][c]{1em}\centering 1\end{minipage} & \makebox[.5em]{$\infty$} & [{\scriptsize\color{ourBlue}59}, {\scriptsize\color{BrickRed}66}] & [{\scriptsize\color{ourBlue}30}, {\scriptsize\color{BrickRed}33}] & [{\scriptsize\color{ourBlue}20}, {\scriptsize\color{BrickRed}22}] & [{\scriptsize\color{ourBlue}15}, {\scriptsize\color{BrickRed}16}] & [{\scriptsize\color{ourBlue}12}, {\scriptsize\color{BrickRed}13}] \\
      \hline
      \begin{minipage}[c][1em][c]{1em}\centering 2\end{minipage} & \makebox[.5em]{$\infty$} & [{\scriptsize\color{ourBlue}119}, {\scriptsize\color{BrickRed}131}] & [{\scriptsize\color{ourBlue}59}, {\scriptsize\color{BrickRed}66}] & [{\scriptsize\color{ourBlue}40}, {\scriptsize\color{BrickRed}44}] & [{\scriptsize\color{ourBlue}30}, {\scriptsize\color{BrickRed}33}] & [{\scriptsize\color{ourBlue}24}, {\scriptsize\color{BrickRed}26}] \\
      \hline
      \begin{minipage}[c][1em][c]{1em}\centering 3\end{minipage} & \makebox[.5em]{$\infty$} & $\infty$ & $\infty$ & $\infty$ & $\infty$ & $\infty$\\
      \hline
    \end{tabular}
\end{table}

@@

\begin{figure}[htb]
\centering
  \includegraphics[width=.48\textwidth]{mapk_model_egf}
\caption{The model represented in the ANIMO user interface.
The \emph{Network} central panel represents the model as the classical nodes-edges network
familiar in biology. To this representation, node colours and shapes are added %in order
to represent current activity levels and protein categories, as defined in the \emph{Legend}
panel on the left. On the right, the \emph{Results Panel} shows a graph of the activities
of selected nodes during the user-chosen interval of 60 minutes.
A vertical red bar, which can be moved with the underlying slider, indicates the point in
the simulation trace on which the colouring of the nodes in the \emph{Network} panel is based.
The graph allows the user to visually compare simulation results with experimental data.
The {\sf Erk (EGF) data} series is based on experimental data from Santos et al.~\cite{egf-ngf}.
}\label{fig:case-study-model}
\end{figure}

@@

\begin{figure}[htb]
\centering
  \includegraphics[width=.48\textwidth]{mapk_model_diff}
\caption{Difference between the simulations obtained using
50 ng/ml NGF and 100 ng/ml EGF as input at 22 minutes (vertical red bar in right panel). In this mode, node colours
are based on the difference of activity between the two configurations of the model:
a red-coloured node is more active due to NGF treatment, while cyan indicates less activity and white
means no difference. Note that NGF and EGF are both white, since at 22 minutes, 
NGF and EGF are inactivated in both conditions by the neutralizing antibody. A slider underneath the graph can be used to 
interactively view the differences at different time points. \label{fig:case-study-diff}}
\end{figure}
